Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-15 automatica/paper.tex
sec 3

%-------------------------------
\subsection{\textcolor{red}{[Elizabeth: please add the specifics of the errors due to discretisation/quantisation, with reference to Fig. \ref{fig:digitalsystem}]}}
%\label{sec:}
%-------------------------------

@@

In this section, we give a brief description of the CEGIS framework, as illustrated in Figure~\ref{fig:CEGIS}.

@@

\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$,
based on the input constraints %\blue{[how is this practically done?With the equation below]}.  
%
\textcolor{red}{[these specifications are (wrongly) introduced only in a later part of the manuscript!]}
$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
\Rightarrow \phi_\mathit{init}^{K}$$
Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.

%-------------------------------
\section{Abstract Acceleration of Linear Dynamics} 
\label{ssec:aa}
%-------------------------------

We recall a recently introduced technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
which will be key in this work for abstraction-based synthesis.  
%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
Given a model of an iterative program with dynamics
%
\begin{equation}
\vec{x}_{k+1}=\mat{A}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
\end{equation}
%
\textcolor{red}{[we should use the notations (with the `d' subscript) in the Preliminaries section.]}
we want to find all possible states visited over an infinite time horizon
starting at an initial set $X_0$.  
This set is known as the \emph{reach tube} of
the model:
%
\begin{equation}
\hat{X} = \{ \vec{x}_k \mid k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A}\vec{x}_k\}.
\end{equation}
%
Using Abstract Acceleration we
transform this problem into a one-step solution.  We first change the
problem statement by means of acceleration into
%
\begin{equation}
\hat{X} = \{ \vec{x}_k=\mat{A}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
\end{equation}
%
and further define new model semantics and corresponding set: 
%
\begin{equation}\label{eq:aa_reachtube}
\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A}^k \subseteq \mathcal{A}, 
\end{equation}
%
where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
over-approximation of the reach tube of the model \cite{JSS14}.  
In this work we use an extension of the abstract acceleration model for
continuous time. 
% and  For this reason we must first look at the acceleration of continuous-time dynamics.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Acceleration of continuous-time models}\label{sec:continuous_time_accel}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
the state of the plant at integer multiples of the sample time.  
%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
However, in
order to synthesize $\mat{K}$, we must be able to ensure that
certain properties \textcolor{red}{[unknown because undefined at this point \ldots]} of the plant hold at any given point in time.  In order
to do so, we accelerate the dynamics of the plant according to the model
semantics in Sec.~\ref{sec:model} and compute the state
$\vec{x}_T$ at a given time $T$,
%
% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
%
namely the state of the system $\dot{\vec{x}}(t)=\mat{A}\vec{x}(t)$ at time
$t=T$.

@@

%-------------------------------
 \subsection{Finding Abstract Supports for Continuous Dynamics}
 \label{sec:cont_aasup}
%-------------------------------

@@

>>>>

%-------------------------------
\subsection{\textcolor{red}{[Elizabeth: please add the specifics of the errors due to discretisation/quantisation, with reference to Fig. \ref{fig:digitalsystem}] and to what has been discussed in the Introductory section.}}
%\label{sec:}
%-------------------------------

@@

In this section, we give a brief description of the CEGIS framework, as illustrated in Figure~\ref{fig:CEGIS}. [ADD REFERENCE(S).]

@@

%-------------------------------
\subsection{Abstract Acceleration of Linear Dynamics} 
\label{ssec:aa}
%-------------------------------

We recall a recently introduced technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
which will be key in this work for abstraction-based synthesis.  
%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
Given a model of an iterative program with dynamics
%
\begin{equation}
\vec{x}_{k+1}=\mat{A_d}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A_d} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
\end{equation}
%
\textcolor{red}{[I have modified the notations with the `d' subscript as above.]}
we want to find all possible states visited over an infinite time horizon
starting at an initial set $X_0$.  
This set is known as the \emph{reach tube} of
the model:
%
\begin{equation}
\hat{X} = \{ \vec{x}_k: k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A_d}\vec{x}_k\}.
\end{equation}
%
Using Abstract Acceleration we transform this sequential reachability problem into a one-step problem.  
We first modify the problem statement by means of acceleration into
%
\begin{equation}
\hat{X} = \{ \vec{x}_k=\mat{A_d}^k\vec{x}_0 : k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
\end{equation}
%
and further define new model semantics and corresponding set: 
%
\begin{equation}\label{eq:aa_reachtube}
\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A_d}^k \subseteq \mathcal{A}, 
\end{equation}
%
where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
over-approximation of the reach tube of the model \cite{JSS14}.  
In this work we extend the abstract acceleration algorithm to continuous-time models. 
% and  For this reason we must first look at the acceleration of continuous-time dynamics.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsubsection{Acceleration of continuous-time models}
\label{sec:continuous_time_accel}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
the state of the plant at integer multiples of the sample time.  
%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
However, in order to synthesize $\mat{K}$, 
we must be able to ensure that given properties of the plant hold at any given point in time.  
In order to do so, we accelerate the dynamics of the plant according to the model
semantics in Sec.~\ref{sec:model} and compute the state
$\vec{x}_T$ at a given time $T$,
%
% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
%
namely the state $\vec{x}(t)$ of the model 
%$\dot{\vec{x}}(t)=\mat{A}
at time $t=T$.

\textcolor{red}{[The following three subsections take too much space, plus the results are mostly known or easily derivable with simple algebra: we need to shorten and simplify it. Dario: can you give it a crack?]}

@@

%-------------------------------
 \subsubsection{Finding Abstract Supports for Continuous Dynamics}
 \label{sec:cont_aasup}
%-------------------------------

\textcolor{red}{[This paragraph is highly unclear - Dario: can you please update it?]}

@@

\textcolor{red}{[Elizabeth: please rewrite this]}

\textcolor{red}{[Dario: once Elizabeth has updated the description of the naive approach, can you update the following part, aligning it with hers?]}

\item Calculate a set of initial bounds on $K$, $\phi_\mathit{init}^{K}$,
based on the input constraints %\blue{[how is this practically done?With the equation below]}.  
%
$$(\phi_\mathit{init} \wedge \phi_\mathit{input} \wedge u_k=-K x_k)
\Rightarrow \phi_\mathit{init}^{K}$$
Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
